Considering scale in multilayer animal social networks

### 2020-06-17 paper/manuscript.Rmd
rest of disc comments

Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Movement as a collective group can reduce per capita
predation risk via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
[@Jolles_2019]. Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
quantify movement parameters could be integrated. For example, edges could
represent measures of dyadic or collective movement based on dynamic interaction
metrics [@Long_2014]. Integrating movement layers with habitat-specific social
association layers could further illuminate the role of movement as a driver
of the social and spatial environments an individual experiences [@Webber_2018].
We generated multilayer networks based on habitat-specific layers of 
social association. Coordinated movement of dyads, or groups, could vary based on
habitat, and the approach we outline could be used to explore mechanisms linking
the social and spatial environments. For example, social processes may be an
emergent property of the landscape because animals aggregate at resources, such
as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
patches or territories can also contribute to the formation of the social
environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
males interacted primarily at home range edges, presumably driving territorial
behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
network framework is a logical next step for a burgeoning field. In particular,
when association networks are habitat-specific, we suggest the integration of
movement and space use in multilayer networks provides novel insights into the
effects of habitat configuration on the formation of the social environment
[@He_2019; @Webber_2018].

@@

Selection of appropriate time windows is essential for capturing sociality in specific
life stages of interest. Social phenotypes can change over ontogeny in ways that
can affect fitness [@Berger_2015; @Brent_2017]. Further complicating the issue,
individuals can vary in their rate of development [@Tarka_2018]. This variation
can make defining the appropriate temporal scale for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny difficult. However, considering fine temporal scales has been show to
provide insight across developmental stages that may otherwise be missed
[@Turner_2017]. Furthermore, given the non-independent nature of social
interactions and associations, especially over time, it can be challenging to
test hypotheses about social dynamics with a suitable null control
[@Farine_2017; @Proskurnikov_2017]. Using the framework of multilayer networks,
ordinal layers of discrete time windows provide a way to make appropriate null
models to test questions about the dynamics of an individual’s social network
position over multiple aggregated time periods.

>>>>

Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Movement as a collective group can reduce per capita
predation risk via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
[@Jolles_2019]. Given the existing framework for constructing multilayer networks from
behavioural layers [e.g. @Smith_Aguilar_2019], monolayer networks that explicitly
quantify movement parameters could be integrated. For example, edges could
represent measures of dyadic or collective movement based on dynamic interaction
metrics [@Long_2014]. Integrating movement layers with habitat-specific social
association layers could further illuminate the role of movement as a driver
of the social and spatial environments an individual experiences [@Webber_2018].
We generated multilayer networks based on habitat-specific layers of 
social association. Coordinated movement of dyads, or groups, could vary based on
habitat, and the approach we outline could be used to explore mechanisms linking
the social and spatial environments.<!--  <- long sentence with two coulds -->For example, social processes may be an 
emergent property of the landscape because animals aggregate at resources, such
as waterholes [@Chamaill_Jammes_2008]. Movement to, from, or within habitat
patches or territories can also contribute to the formation of the social
environment [@Spiegel_2016]. For example, in sleepy lizards (*Tiliqua rugosa*)
males interacted primarily at home range edges, presumably driving territorial
behaviour [@Spiegel_2018]. Incorporating movement ecology within a multilayer
network framework is a logical next step for a burgeoning field. In particular,
when association networks are habitat-specific, we suggest the integration of
movement and space use in multilayer networks provides novel insights into the
effects of habitat configuration on the formation of the social environment
[@He_2019; @Webber_2018].

@@

Selection of appropriate time windows is essential for capturing sociality in specific
life stages of interest. Social phenotypes can change over ontogeny in ways that
can affect fitness [@Berger_2015; @Brent_2017]. Further complicating the issue,
individuals can vary in their rate of development [@Tarka_2018]. This variation
can make defining the appropriate temporal scale for testing the fitness
implications of an individual’s social phenotype over different stages of
ontogeny difficult. However, considering fine temporal scales has been show to
provide insight across developmental stages that may otherwise be missed
[@Turner_2017] <!-- It would be better to cite the more recent one if it gets released in time. --> 
Furthermore, given the non-independent nature of social
interactions and associations, especially over time, it can be challenging to
test hypotheses about social dynamics with a suitable null control
[@Farine_2017; @Proskurnikov_2017]. Using the framework of multilayer networks,
ordinal layers of discrete time windows provide a way to make appropriate null
models to test questions about the dynamics of an individual’s social network
position over multiple aggregated time periods.
